---
title: "p8105_hw5_nl2835"
author: "Nancy Le"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(collapse = TRUE, message = FALSE)
library(purrr)

```


```{r load csv file}
homicides <-
  read.csv("./local/homicide-data.csv") |> 
  janitor::clean_names() |> 
  separate(reported_date, into = c("year", "month", "day"), sep = c(4,6))  
```

## Problem 1

The raw data describes victim name, race, age, sex, location of homicide, and whether an arrest was made.

```{r}
homicides = homicides |> 
  mutate(city_state = paste(city, state, sep = ", ")) |> 
  group_by(city_state) 

```

```{r count number of homicides}
homicides |> 
  summarize(count = n())
```

There are `r nrow(homicides)` homicides from 2010 to 2016.

```{r}
homicides |> 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") |> 
  summarize(count = n())
```

There are `r nrow(homicides |> filter(disposition == "Closed without arrest" | disposition == "Open/No arrest"))` unsolved homicides. 


```{r df unsolved}
baltimore = homicides |> 
  filter(city_state == "Baltimore, MD") |> 
  mutate(
    unresolved = as.numeric(disposition == "Closed without arrest" | disposition == "Open/No arrest")) |> 
  select(city_state, unresolved, everything()) |> 
  group_by(unresolved) |> 
  summarize(number = n()) |> 
  mutate(total = sum(number)) |> 
  filter(unresolved == 1) |> 
  select(number, total)
```

```{r prop test}
baltimore_pt = 
  prop.test(baltimore$number, baltimore$total) |>
  broom::tidy() |> 
  janitor::clean_names()

baltimore_pt |> 
  select(estimate, conf_low, conf_high) |> knitr::kable()
```

The estimated proportion of homicides unsolved is 0.6456 with a confidence interval of [0.627, 0.663].

**do rest of prop tests for each city later

## Problem 2

```{r tidy df with all participants}
names = list.files(path="./local/data", full.names=TRUE)

readin_csv = function(path) {
  df =
    read_csv(path) |>
    janitor::clean_names() |>
    mutate(
      id = path
    ) |> 
    mutate(arm = substr(id, 14, 16), id = substr(id, 18, 19))
} |> 
  select(everything())

output = map(names, readin_csv) |> bind_rows()

```

```{r tidy further}
output = output |> 
  pivot_longer(week_1:week_8,
               names_to = "week", 
               values_to = "value") |> 
  mutate(week = substr(week, 6, 7))
```

```{r spaghetti plot}
output |> 
  mutate(week = as.numeric(week)) |> 
  ggplot(aes(x = week, y = value, color = id)) + geom_line() + facet_grid(~arm)
```

The experimental arm had higher average values overall and an increase over time, compared to the control arm that had lower average values and a decrease over time. 




